Supplementary material

### 2021-06-29 submission/supplement.rmd
add performance metrics in gusto

---
title: "Supplementary material"
output:
    bookdown::pdf_document2: default
geometry: margin=1.0in
toc: false
font-size: 12pt
header-includes:
  - \usepackage{amssymb}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \newcommand\given[1][]{\:#1\vert\:}
editor_options: 
  chunk_output_type: console
bibliography: references.bib
csl: jce.csl
---

@@

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Smooth calibration of the derived prediction model."}
gustoModelData <- gusto %>%
  rename(
    "outcome" = "day30",
    "treatment" = "tpa"
  )

@@

predictionStats <- rms::val.prob(
  y = gustoModelData$outcome, 
  logit = prediction$linear.predictors,
  logistic.cal = FALSE,
  statloc = FALSE
)
```

```{r modelCoefficients, echo=FALSE, warning=FALSE, message=FALSE}

@@

@@

 knitr::kable(
    table,
    format      = "latex",
    align       = "r",
    booktabs    = TRUE,
    digits      = 4,
    format.args = list(
      big.mar      = ",",
      decimal.mark = "."
    ),
    caption    = "Evaluation statistics of the prediction model for 30-day mortality in GUSTO-I."
  ) 
```

>>>>

---
title: "Supplementary material"
output:
    bookdown::pdf_document2: default
geometry: margin=1.0in
toc: false
font-size: 12pt
header-includes:
  - \usepackage{amssymb}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \newcommand\given[1][]{\:#1\vert\:}
  - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}

editor_options: 
  chunk_output_type: console
bibliography: references.bib
csl: jce.csl
---

@@

\beginsupplement

@@

```{r modelCoefficients, echo=FALSE, warning=FALSE, message=FALSE}
gustoModelData <- gusto %>%
  rename(
    "outcome" = "day30",
    "treatment" = "tpa"
  )

@@

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Smooth calibration of the derived prediction model."}
predictionStats <- rms::val.prob(
  y = gustoModelData$outcome, 
  logit = prediction$linear.predictors,
  logistic.cal = FALSE,
  statloc = FALSE
)
```

@@

 knitr::kable(
    table,
    format      = "latex",
    align       = "l",
    booktabs    = TRUE,
    digits      = 4,
    format.args = list(
      big.mar      = ",",
      decimal.mark = "."
    ),
    caption    = "Evaluation statistics of the prediction model for 30-day mortality in GUSTO-I."
  ) 
```

We used the derived prediction model to predict benefit of tPA to 30-day
mortality using the data at hand. The models are presented in the main
manuscript. All approaches displayed comaprable discrimination for benefit, with
the constant treatment effect model, the linear interaction model and the RCS (5
knots) model displaying the highest performance (Table
\@ref(tab:gustoPerformanceMetrics)). However, the linear interaction model and
the RCS (5 knots) model were worse calibrated. The constant treatment effect
model also had the best performance among the considered methods in terms of
calibration for benefit.

```{r gustoPerformanceMetrics, echo=FALSE, warning=FALSE, message=FALSE}
metrics <- readr::read_csv(
  here::here("data/processed/gustoPerformanceMetrics.csv")
)

 knitr::kable(
    metrics,
    format      = "latex",
    align       = "l",
    booktabs    = TRUE,
    digits      = 4,
    format.args = list(
      big.mar      = ",",
      decimal.mark = "."
    ),
    col.names = c(
      "Model",
      "C",
      "ICI"
    ),
    caption    = "Performance metrics of the different methods used to predict benefit of tPA on 30-day mortality using data from the GUSTO-I trial."
  ) 
```
